---
title: "Multiple Linear Regression"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

# Regression Notebook
Notebook for exploring topics in MLR. Import packages needed:
```{r}
library(ggplot2)
library(tidyverse)
library(dplyr)
library(tidyr)
library(leaps)
library(stargazer)
```
## Data Import
Import data directly from [data.world](https://data.world/nrippner/ols-regression-challenge) website. Follow link to see description of features.
```{r}
df <- read.csv("https://query.data.world/s/2jv7merfywlkqib4cspioa4zrf25eu", header=TRUE, stringsAsFactors=FALSE)
```

## Exploratory DataAnalysis {.tabset .tabset-fade .tabset-pills}
### Missing Data  
We will want to start by assessing any missing data, and determining if the features will be filled or dropped based on their missing value counts.
```{r}
colnames(df)[apply(df, 2, anyNA)]

sum(is.na(df["PctSomeCol18_24"])) # 2285 of 3047 values missing (DROP FEATURE)
sum(is.na(df["PctEmployed16_Over"])) # 152 of 3047 values missing (FILL)
sum(is.na(df["PctPrivateCoverageAlone"])) # 609 of 3047 values missing (FILL)
```
The *PctSomeCol18_24* is missing around 75% of its data, so it will be dropped from the inputs. The *PctEmployed16_Over* has a slight left skew but was approximately normally distributed, so the missing values will be filled with median (same value as mean but was rounded to 1 decimal place). *PctPrivateCoverageAlone* was normally distributed, and will be filled with its median value as well.
```{r}
median.ppca.fill <- median(df[,"PctPrivateCoverageAlone"], na.rm=TRUE) # 48.7
median.pe16.fill <- median(df[,"PctEmployed16_Over"], na.rm=TRUE) # 54.5

df <- df %>% mutate(PctPrivateCoverageAlone = ifelse(is.na(PctPrivateCoverageAlone), 
                                                     median.ppca.fill, 
                                                     PctPrivateCoverageAlone),
                    PctEmployed16_Over = ifelse(is.na(PctEmployed16_Over), 
                                                median.pe16.fill, 
                                                PctEmployed16_Over))

df$PctSomeCol18_24 <- NULL # Drop column
any(is.na(df))
```


### Outliers  
From a quick check by summary table (omitted from report for size of output) it seems that *popEst2015*, *studyPerCap*, *MedianAge*, *PctBachDeg18_24*, *PctNoHS18_24*, *PctAsian*, and *PctOtherRace* all have outliers well above their 3rd Quartile. We will need to look into these features to make sure there was not an error in the data recording process.

```{r}
outlier.check <- c('popEst2015', 'studyPerCap', 'MedianAge', 'PctBachDeg18_24', 
                   'PctNoHS18_24', 'PctAsian', 'PctOtherRace')
outlier.df <- data.frame(Feature=outlier.check, Quantile90=NA)

for (idx in 1:7) { outlier.df[idx,2] <- round(unname(quantile(df[,outlier.check[idx]], 0.90)), 2) }
outlier.df

ggplot(gather(df[outlier.check]), aes(value)) + geom_histogram() + facet_wrap(~key, scales = 'free_x')
```

### Part 3 
```{r}
# Code here
```

### Part 4 
```{r}
# Code here
```


## Data Preprocessing {.tabset .tabset-fade .tabset-pills}
### Part 1
```{r}
# Code here
```

### Part 2 
```{r}
# Code here
```

### Part 3 
```{r}
# Code here
```

### Part 4 
```{r}
# Code here
```



## Modeling {.tabset .tabset-fade .tabset-pills}
### Model Setup
```{r}
# Code here
```

### Assumption Checks
```{r}
# Linearity, Constant Variaibility (homoscedasticity), Normality of Residuals
```

### Part 3 
```{r}
# Code here
```


## Conclusion

