---
title: "Multiple Linear Regression"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message=FALSE)
```

# Regression Notebook
Notebook for exploring topics in MLR. Import packages needed:
```{r}
library(ggplot2)
library(dplyr)
library(tidyr)
library(leaps)
library(stargazer)
```
## Data Import
Import data directly from [data.world](https://data.world/nrippner/ols-regression-challenge) website. Follow link to see description of features.
```{r}
df <- read.csv("https://query.data.world/s/2jv7merfywlkqib4cspioa4zrf25eu", header=TRUE, stringsAsFactors=FALSE)
```

## Exploratory Data Analysis {.tabset .tabset-fade .tabset-pills}
### Part 1
```{r}
# Code here
```

### Part 2 
```{r}
# Code here
```

### Part 3 
```{r}
# Code here
```

### Part 4 
```{r}
# Code here
```


## Data Preprocessing {.tabset .tabset-fade .tabset-pills}
### Part 1
```{r}
# Code here
```

### Part 2 
```{r}
# Code here
```

### Part 3 
```{r}
# Code here
```

### Part 4 
```{r}
# Code here
```



## Modeling {.tabset .tabset-fade .tabset-pills}
### Part 1
```{r}
# Code here
```

### Part 2 
```{r}
# Code here
```

### Part 3 
```{r}
# Code here
```


## Conclusion

